<div class="container">
<p class="intro"></p>

# Title
# Name
# Affiliation
```{r setup, include=FALSE}
# set global chunk options
library(knitr); library(knitcitations); library(reports); library(ggplot2)
library(rCharts); library(xtable)

opts_chunk$set(
	tidy = FALSE,
    cache=FALSE
)

write.bibtex(c(                         ## temp bib delete these lines
	rinker2013 = citation("reports"), 
	ramnath2013 = citation("slidify"),
    xie2013 = citation("knitr")
))                                                
bib <- read.bibtex("knitcitations.bib") ## temp bib delete these lines
#bib <- read.bibtex(file.path(getwd(), basename(getOption("bib.loc"))))
#cite in text using `r citet(bib[1])`
```

<hr class="breaks">

# Abstract
# *Keywords:*

<hr class="breaks">

## Introduction paragraphs...

<p class="stan">Be sure to run the `r CN("custom_css")` function to style the RStudio preview html.</p>

... research questions:

1.    
2.	 

### Level 3 Header. 

```{r fig.cap = "A caption"}
ggplot(mtcars, aes(mpg, hp, color=as.factor(cyl))) + geom_point(size=3)
```
`r cap(1, "scatter1", "A simple ggplot image.")`

### Level 3 Header. 

> Here's a block quote... 

<p class="stan">Content here.  Created using the reports package `r citep(bib[["rinker2013"]])`.  I've done my best to maintain APA6 standards in this document but within HTML5 some rules do not make sense.  For instance, there are no page breaks.</p>

<hr class="breaks">

## Method
### Participants.
### Research Design. 
### Measures.
### Procedure. 

<hr class="breaks">

## Results
### Level 3 Header.
#### Level 4 Header.
##### Level 5 Header.

<hr class="breaks">

## Discussion

I can embed a video (see `r HR("#youtube", "Figure 2")`).

`r YT("ArHQjQyIS70")`

`r cap(1, "youtube", "A YouTube video.")`

Using rCharts is easy too (see `r HR("#rchart", "Figure 3")`).


``````{r nvd3plot2, results = 'asis', comment = NA, message = FALSE, echo = TRUE} 
hair_eye_male <- subset(as.data.frame(HairEyeColor), Sex == "Male")
n1 <- nPlot(Freq ~ Hair, group = "Eye", data = hair_eye_male, type = 'multiBarChart')
n1$set(width = 800, height=600)
n1
```

`r cap(1, "rchart", "An rChart.")`

### Implications.

<p class="stan">We have a nice view of `r HR("#mtcars", "Table 1")`.  Here we use the `r HR("", "texreg")` package as seen in the following code:</p>  

```{r, results="hide", message=FALSE}
library(nlme); library(texreg)
model.1 <- lme(distance ~ age, data = Orthodont, random = ~ 1)
model.2 <- lme(distance ~ age + Sex, data = Orthodont, random = ~ 1)

htmlreg(list(model.1, model.2),  
    inline.css = FALSE, doctype = FALSE, caption = "",
    head.tag = TRUE, body.tag = TRUE)
```

And then the output:

`r cap(2, "mtcars", "A Nice Little texreg Output", style="margin-top: 3em;")`
```{r, results="asis", echo = FALSE}
htmlreg(list(model.1, model.2),  
    inline.css = FALSE, doctype = FALSE, caption = "",
    head.tag = TRUE, body.tag = TRUE)
```

### Limitations.

### Conclusions. 

<p class="stan">Yihui `r citet(bib[["xie20132"]])` and Ramnath `r citet(bib[["ramnath2013"]])` and others have created terrific report and presentation framework.</p>

<hr class="breaks">

# References
<div class="hangingindent" style="padding-top:.5%;">  

<p style="padding-top:0%;">
```{r, echo=FALSE, results='asis'}
bibliography("html", bulleted = FALSE) 
```
</p>

<p class = "end"></p>

