---
title       : reports package
subtitle    : Quick Start Guide
author      : Tyler Rinker
logo        : reports.PNG
job         : 
framework   : io2012       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]
mode        : selfcontained #standalone
--- dt:10

```{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(cache=FALSE)
## library(slidify); library(slidifyLibraries)
library(knitr); library(knitcitations); library(reports)
#write.bibtex(c(Francois2013= citation("bibtex"), "Yihui2013" = citation("knitr"), 
#    "Boettiger2013" = citation("knitcitations"), "Rinker2013b" = citation("reports"), 
#    "Rinker2013a" = citation("qdap"), "Vaidyanathan2012" = citation("slidify")), 
#    file = "reports.bib")
bib <- read.bibtex("reports.bib")
```
<style>
body {
  background-color: #000;
}
.quiz-option label{
  display: inline;
  font-size: 1em;
}
.refs {
  padding-left: 80px;
  text-indent: -35px;
}
</style>

## Purpose
reports `r citep(bib[6])` is a package that assists in writing flexible reports
and presentations.  The package is designed to be used with RStudio,
MiKTex/TexLive/LibreOffice, Pandoc, knitr `r citep(bib[4])`, slidify 
`r citep(bib[8])` and knitcitations `r citep(bib[5])`.  
</br> 
`r IM("https://dl.dropboxusercontent.com/u/61803503/packages/reports.PNG", width=670, height=550)`

--- &twocol

## Why reports ##
</br>
`r FT(22, text="reports Will Make You...")`

*** =left
</br>
>- `r FT(22, red, text="Efficient")`
>- `r FT(22, red, text="Organized")`    
>- `r FT(22, red, text="Consistent")`     
>- `r FT(22, red, text="Happy")` 

*** =right
`r VS(2)`
`r IM("http://png-1.findicons.com/files/icons/350/aqua_smiles/128/fun.png", width=230, height=150)`


---

## Getting Started

**Download:**    
* RStudio - [http://www.rstudio.com/](http://www.rstudio.com/)       
* MiKTex - [http://miktex.org/](http://miktex.org/) or    
* TexLive - [http://www.tug.org/texlive/](http://www.tug.org/texlive/)   
* LibreOffice - [http://www.libreoffice.org/](http://www.libreoffice.org/)   
* Pandoc - [http://johnmacfarlane.net/pandoc/](http://johnmacfarlane.net/pandoc/)     
* knitr (Xie, 2013) - [http://yihui.name/knitr/](http://yihui.name/knitr/) 
* slidify (Vaidyanathan, 2012) - [http://ramnathv.github.io/slidify/](http://ramnathv.github.io/slidify/)   
* knitcitations (Boettiger, 2013)    
<hr color="green" size="3">

```{r inst, include=TRUE, eval=FALSE}
install.packages("reports")
```
*This will install: knitr, knitcitations & slidify too*

---

## Windows Users...

may want to use:

```{r inst2, include=TRUE, eval=FALSE}
install.packages("installr")
```

---

## Development Version Installation

`r HR("https://github.com/trinker/reports", "https://github.com/trinker/reports")` 

```{r inst3, include=TRUE, eval=FALSE}
library(devtools)         
install_github("reports", "trinker") 
```

---

## Set Up .Rprofile ##

The user can add these options to their .Rprofile       

```{r inst4, include=TRUE, eval=FALSE}
options(bib.loc = "C:/Users/trinker/Desktop/PhD Program/MASTER.bib")    
options(name.reports = "Tyler Rinker\\\\University at Buffalo")
options(sources.reports = path.expand("~/path_1"), path.expand("~/path_2"))  
options(temp.reports = "apa6.mod.qual_tex")
options(github.user = "trinker")   
options(speed.temp = list(`1`="wordpress_rmd", `2`="basic_rmd", `3`="apa6.mod.qual_tex"))
options(present.template = "revealjs")
```


---

## Create Report/Paper Project ##
### Now the user is ready to generate a new report/paper or presentation project.  

Use:    
```{r proj, include=TRUE, eval=FALSE}
setwd(desired.location)   
new_report("NEW")

#or

presentation("NEW")
```

---

## Get Started!

`r HR2("http://dl.dropboxusercontent.com/u/61803503/packages/reports_vignette.html", "reports_vignette")`  
`r HR2("http://trinker.github.io/reports/", "reports Web Page")`    
`r HR2("http://dl.dropbox.com/u/61803503/report_directory_guide.pdf", "Project Directory Workflow")`     
`r HR2("http://trinker.github.io/reports/dependencies", "reports Dependencies")`      
`r HR2("http://dl.dropboxusercontent.com/u/61803503/Slides/reports/reports_quick_slides.txt", ".Rmd file of these slides")`  
`r HR2("https://github.com/ramnathv/slidifyExamples", "Slidify Examples")` 

--- .YT yt:ArHQjQyIS70 &youtube


--- .refs
## References
```{r, echo=FALSE, results='asis'}
bibliography("html", bulleted = FALSE)
```
