---
title: rNVD3
subtitle: Interactive Charts from R using NVD3.js
author: Ramnath Vaidyanathan
url: {lib: ../../libraries}
framework: io2012
highlighter: highlight.js
hitheme: github
widgets: [quiz, bootstrap, nvd3]
mode: standalone
github:
  user: ramnathv
  repo: rNVD3
---

## Introduction

`rNVD3` is an R package that provides a familiar plotting interface to create interactive visualizations using [NVD3.js](http://nvd3.org)

You can install `rNVD3` from `github` using the `devtools` package

```{r eval = F}
require(devtools)
install_github('rNVD3', 'ramnathv')
```

Here is an example that you can try in your R console

```{r eval = F}
hair_eye = subset(as.data.frame(HairEyeColor), Sex == "Female")
p1 <- nvd3Plot(Freq ~ Hair | Eye, data = hair_eye, type = 'multiBarChart')
p1$chart(color = c('brown', 'blue', '#594c26', 'green'))
p1
p1$save('haireye.html')
```


---

<style>
.nvd3Plot {
  background-color: #eee;
  width: 900px;
  height: 500px;
  margin: auto auto;
  display: block;
}
</style>

```{r echo = F, message = F}
opts_template$set(nvd3 = list(comment = NA, results = 'asis', message = F, warning = F, tidy = F, echo = T))
require(rNVD3)
```

## Bar Chart (Discrete)

```{r discreteBar, opts.label = 'nvd3'}
bar1 <- nvd3Plot(~ gear, data = mtcars, type = 'discreteBarChart')
bar1$printChart()
```

*** =code

```{r ref.label = 'discreteBar', eval = F}
```

---


## Bar Chart (Dodged/Stacked)


```{r multiBarChart, opts.label = 'nvd3'}
data('tips', package = 'reshape2')
bar2 <- nvd3Plot(~ day | sex, data = tips, type = 'multiBarChart')
bar2$printChart('barChart')
```

---

## Bar Chart (Horizontal)


```{r multiBarHoriz, opts.label = 'nvd3'}
bar2$addParams(type = 'multiBarHorizontalChart')
bar2$printChart('horizontalBar')
```


---

## Scatter Chart

```{r opts.label = 'nvd3'}
p1 <- nvd3Plot(mpg ~ wt | cyl, data = mtcars, type = 'scatterChart')
p1$xAxis(axisLabel = 'Weight')
p1$printChart()
```

---

## Line Chart

```{r lineChart, opts.label = 'nvd3'}
data(economics, package = 'ggplot2')
ecm <- reshape2::melt(economics[,c('date', 'uempmed', 'psavert')], id = 'date')
p2 <- nvd3Plot(value ~ date | variable, data = ecm, type = 'lineChart')
p2$printChart('lineChart')
```

---

## Line with Focus Chart

```{r lineWithFocusChart, opts.label = 'nvd3'}
p2$addParams(type = 'lineWithFocusChart')
p2$printChart('lineWithFocus')
```

---

## Cumulative Line Chart

```{r cumulativeLineChart, opts.label = 'nvd3'}
p2$addParams(type = 'cumulativeLineChart')
p2$printChart('cumulativeLineChart')
```


---

## Stacked Area Chart

```{r opts.label = 'nvd3'}
p2$addParams(type = 'stackedAreaChart', id = 'stackedArea')
p2$printChart('stackedArea')
```

---

## Pie Chart

```{r opts.label = 'nvd3'}
haireye <- subset(as.data.frame(HairEyeColor), Sex == "Female" & Hair == "Blond")
pie1 <- nvd3Plot(Freq ~ Eye, data = haireye, type = 'pieChart')
pie1$printChart()
```

---

## Donut Chart

```{r opts.label = 'nvd3'}
pie1$chart(donut = TRUE)
pie1$printChart('donutChart')
```




