---
title      : <%= group %>
subtitle   : 
author     : 
job        : 
logo       : 
biglogo    : 
license    : 
framework  : io2012
highlighter: highlight.js
hitheme    : tomorrow
mode       : selfcontained
widgets    : [mathjax, quiz, bootstrap]
---
```{r setup, include=FALSE}
packs <- c("reports", "knitr", "brew", "tools", "slidify", "xtable", 
    "slidifyLibraries", "knitcitations")
invisible(lapply(packs, require, character.only = TRUE))

opts_chunk$set(cache=FALSE)
## Set the path to save figures to be unique for each of the reports; 
## otherwise unnamed chunks will get overwritten.
opts_chunk$set(fig.path = 'assets/fig/<%= group %>-')

BIB <- system.file("extdata/docs/example.bib", package = "reports") #test .bib
bib <- read.bibtex(BIB)
#
#Reading in your own bib file:
#bib <- read.bibtex(dir()[tools::file_ext(dir()) == "bib"][1])
#cite in text using `r citet(bib[1])`
```
<style>
body {
  background-color: #000;
}
.quiz-option label{
  display: inline;
  font-size: 1em;
}
.refs {
  padding-left: 80px;
  text-indent: -35px;
}
ul.nav li::before { content: ""; } 
ul.nav li{ font-size: 18px; line-height: 24px;}
</style>


## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Cylinder <%= group %>

```{r, results="asis", echo=FALSE}
mydf <- mtcars[mtcars$cyl == <%= group %>, ]
print(xtable(mydf), type="html", include.rownames = FALSE)
```

---

## Heat of cyl = <%= group %>

```{r message = F, fig.height = 5}
heatmap(as.matrix(mtcars[mtcars$cyl == <%= group %>, ]))
```

---

## What Next?

After you've developed a template run the functions in the `brew.R` file found in the main directory.

--- .refs

## References
```{r, echo=FALSE, results='asis'}
bibliography("html", bulleted = FALSE)
```
