---
title      : 
author     : 
framework  : deckjs
deckjs     :
  theme: web-2.0
highlighter: highlight.js
hitheme    : solarized_light
mode       : selfcontained
widgets    : [mathjax, quiz, bootstrap]
---
```{r setup, include=FALSE}
# set global chunk options
library(reports); library(slidify); library(knitcitations); library(knitr)
opts_chunk$set(cache=FALSE)
BIB <- system.file("extdata/docs/example.bib", package = "reports") #test .bib
bib <- read.bibtex(BIB)
#
#Reading in your own bib file:
#bib <- read.bibtex(dir()[tools::file_ext(dir()) == "bib"][1])
#cite in text using `r citet(bib[1])`
```
<style>
body {
  background-color: #000;
}
.quiz-option label{
  display: inline;
  font-size: 1em;
}
.refs {
  padding-left: 80px;
  text-indent: -35px;
}
ul.nav li::before { content: ""; } 
ul.nav li{ font-size: 18px; line-height: 24px;}
</style>


## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Slide 2

For slidify framework examples run:    
browseURL("https://github.com/ramnathv/slidifyExamples/tree/gh-pages/examples/deckjs")   
browseURL("http://ramnathv.github.io/slidifyExamples/examples/deckjs/")

`r citet(bib[3])`

--- .YT yt:ArHQjQyIS70 &youtube

--- .refs

## References
```{r, echo=FALSE, results='asis'}
bibliography("html", bulleted = FALSE)
```
