---
title      : 
subtitle   : 
author     : 
job        : 
logo       : 
biglogo    : 
license    : 
framework  : revealjs
highlighter: highlight.js
hitheme    : solarized
revealjs:
  center: "true"
mode       : selfcontained
bootstrap:
  theme: amelia
---
```{r setup, include=FALSE}
# set global chunk options
library(reports); library(slidify); library(knitcitations); library(knitr)
opts_chunk$set(cache=FALSE)
BIB <- system.file("extdata/docs/example.bib", package = "reports") #test .bib
bib <- read.bibtex(BIB)
#
#Reading in your own bib file:
#bib <- read.bibtex(dir()[tools::file_ext(dir()) == "bib"][1])
#cite in text using `r citet(bib[1])`
```
<style>
.refs {
  padding-left: 80px;
  text-indent: -35px;
}
ul.nav li::before { content: ""; } 
ul.nav li{ font-size: 18px; line-height: 24px;}
</style>

# title
### name
### `r as.character(Sys.Date())`

---  ds:blue

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

`r VS(2)` `r FT(3, text="PS see PRESENTATION/assets/css/style.css to add slide colors")`

--- .class #id 

## Slide 2

For slidify framework examples run:    
browseURL("https://github.com/ramnathv/slidifyExamples/tree/gh-pages/examples/revealjs")    
browseURL("http://ramnathv.github.io/slidifyExamples/examples/revealjs/#/slide-1")

`r citet(bib[1])`

---

`r YT("kws1PX1Dw9w")`

--- .refs
## References
```{r, echo=FALSE, results='asis'}
bibliography("html")
```
