<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{A Markdown Vignette with knitr}
-->

```{r setup, include=FALSE}
# set global chunk options
library(knitr)
opts_chunk$set(cache=FALSE)
library(knitcitations); library(reports)
#bib <- read.bibtex(file.path(getwd(), basename(getOption("bib.loc"))))
#cite in text using `r citet(bib[1])`
```
# vignette_name
## name
### `r as.character(format(Sys.Date(), "%m-%d-%Y"))`

To enable Markdown vignettes in an R package, you need to

- add `*.Rmd` files under the `inst/doc` or `vignettes` directory
- add `VignetteBuilder: knitr` to the `DESCRIPTION` file
- specify the vignette engine `\VignetteEngine{knitr}` in the `Rmd` files (inside HTML comments)

You can use your own CSS file instead of the built-in style in the **markdown** package -- just set the option `markdown.HTML.stylesheet`, e.g.

```{r css, echo = FALSE}
options(markdown.HTML.stylesheet = "css/style.css")
```

## References
```{r, echo=FALSE, results='asis'}
#bibliography("html") 
```