---
title:  "vignette_name"
author: "name"
date:   '`r Sys.Date()`'
output: 
  html_document:
    css: assets/fix-bootstrap.css
    toc: yes  
    pandoc_args: [
      "--biblio", "references.bib"
      ]
---

<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{A Markdown Vignette with knitr}
-->

```{r setup, include=FALSE}
# set global chunk options
library(knitr)
opts_chunk$set(cache=FALSE)

library(knitcitations); library(reports)
cleanbib()
options("citation_format" = "pandoc")
```

To enable Markdown vignettes in an R package, you need to

- [ ] add `*.Rmd` files under the `inst/doc` or `vignettes` directory
- [ ] add `VignetteBuilder: knitr` to the `DESCRIPTION` file
- [ ] specify the vignette engine `\VignetteEngine{knitr}` in the `Rmd` files (inside HTML comments)

You can use your own CSS file instead of the built-in style in the **markdown** package -- just set the css in the yaml.


## References
```{r, echo=FALSE, message=FALSE}
#write.bibtex(file="references.bib")
```

```{r clean-up, include=FALSE}
# R compiles all vignettes in the same session, which can be bad
rm(list = ls(all = TRUE))
```
